Summarize twas: chr17 to 22

### 2020-09-23 analysis/simulation-multi-ukbchr17to22-gtex.adipose_susieprior.Rmd
susie prior

@@

* The prior used is: 
```{r  par1}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

```{r cali 2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par1 a}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1 a, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

```{r cali 2 a, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par1-2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par2-2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 2-2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par3.2.1}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 3.2.1, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par 3.2.2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 3.2.2, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

>>>>

# Test true prior

## Regions rPIP > 0.5, simulation 1-x
```{r output-t dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.5/"
```

We run 50 simulations and run susie using the true parameter (gene and snp pi1) as prior. We run susie for regions with regional sum of pip from mr.ash2s for both genes and snps > 0.5. run susie with L=1.

### Truth

* The true parameters we used to simulate data: 
```{r  true par-t}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_2.txt"), header = T)
t(par[,2, drop = F])
```

### Use truth as prior

* The prior used is: 
```{r  par1-t}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.5/"
```
* susie results: 
```{r cali 1-t, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3)); cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP"); cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP"); cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

## Causal regions, simulation 3-x
We run susie for regions with causal signals. run susie with L=1.

### Truth

* The true parameters we used to simulate data: 
```{r  true par-t3}
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-3-fixprior_causal/"
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[,2, drop = F])
```

### Use truth as prior

* The prior used is: 
```{r  par1-t3}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-t3, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3)); 
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

# Test over and underestimated gene pi1
We intentionally use over or underestimated gene pi1 and use the same snp pi1 (close to truth) when running SUSIE. Run susie `L=1`.

## Causal regions, simulation 3-x

* The true parameters we used to simulate data: 
```{r  par-over-t}
susiedir <- "/home/simingz/causalTWAS/simulations/simulation_susietest_20200721/20200721-3-fixprior_causal/"
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[,2, drop = F])
```

### Use overestimated gene pi1

* The prior used is: 
```{r  par1-t3-over}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-t3-over, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior1.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

### Use underrestimated gene pi1

* The prior used is: 
```{r  par1-t3-under}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_3.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-t3-under, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior3.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par1}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

```{r cali 2, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par1 a}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1 a, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

```{r cali 2 a, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3)) 
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par1-2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1-2, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par2-2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 2-2, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par3.2.1}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 3.2.1, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3))
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par 3.2.2}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 3.2.2, fig.height=4, fig.width=12}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))
par(mfrow=c(1,3)) 
cp_plot(res$pip.null, res$ifcausal, main = "SUSIE.uniform PIP")
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```
